\documentclass[a4paper, twoside, 12pt, noanswers]{exam}


% \documentclass[a4paper, 12pt, answers]{exam}
\usepackage{fontspec}

\usepackage{polyglossia}
\usepackage{dirtytalk}
\usepackage{enumitem}
\usepackage{fancybox}
\usepackage{multicol}
\usepackage{framed}

\setdefaultlanguage{english}


\setotherlanguage{hindi}
\newfontfamily\devanagarifont[Script=Devanagari]{Shobhika} % Shobhika, Mukta, Kalimati, Lohit Devanagari, Lohit Nepali

\defaultfontfeatures{Ligatures=TeX}


\newcommand{\textnp}{\texthindi}
\newenvironment{nepali}{\begin{hindi}}{\end{hindi}}



\usepackage[onehalfspacing]{setspace}
\usepackage{graphicx}
\usepackage{multicol,adjustbox}

% \pointsinrightmargin %points in right margin
% \bracketedpoints

\nopointsinmargin
\pointformat{}

\unframedsolutions


\CorrectChoiceEmphasis{\bfseries\boldmath}
\renewcommand{\thepartno}{\alph{partno}}
\renewcommand{\thesubpart}{(\Roman{subpart})}
\renewcommand{\subpartlabel}{\thesubpart} 
\renewcommand{\choicelabel}{(\alph{choice})}
\thispagestyle{empty}

% \title{\vspace{-1.7cm} 
% 	\hrule
% 	\vspace*{0.2cm}

% 	{\bfseries\LARGE PURBANCHAL UNIVERSITY \\2018}\\[2mm]
% 	{\large 4 Years Bachelor of Computer Application (BCA/Eighth Semester/Final)}\\[2mm]	  
% 	{\large Time: 3.00 hrs.  \hfill Full Marks: 60 /Pass Marks: 24}\\[2mm]
% 	{\large \bfseries {BCA452CO, Multimedia Application \hfill {}}}\\[2mm]
% 	\hrule
% }
% \date{}

\cfoot[]{}
\clearpage

\begin{document}
% \maketitle\vspace{-2.5cm}

\begin{framed}
	\raggedright{\bfseries\Large\centering PURBANCHAL UNIVERSITY \par {2018/ \textnp{२०७५}}\par}
	{ 4 Years Bachelor of Computer Application (BCA/Eighth Semester/Final)\par}
	{ Time: 3.00 hrs.  \hfill Full Marks: 60 / Pass Marks: 24\par}
	{\bfseries {BCA452CO, Multimedia Application\hfill}\par}
\end{framed}

{\noindent \it{Candidates are required to give their own answers in their own words as far as practicable.  }\par}
{\noindent \it{Figure in the margin indicate full marks.}\par}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\fullwidth{\centering \bfseries \underline{Group A}}}
{\hspace*{-0.5cm} \bfseries Answer TWO questions.} \hfill {\( \mathbf{2\times 12 =24}\)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}

\question How image and graphics is represented in PC? Describe image
synthesis and image analysis. Explain image recognition steps
with the help of block diagram.

\question
\begin{parts}
	\part Explain importance of data compression with its issues. Compare
	source coding, entropy coding, and hybrid coding.
	\part Describe video compression techniques used in MPEG system.
\end{parts}

\question What is data conversion? Explain with example. Briefly discuss
the concept of interface.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\fullwidth{\centering \bfseries \underline{Group B}}\par}
{\hspace*{-0.5cm}\noindent\bfseries Answer SIX questions.} \hfill {\( \mathbf{6 \times 6 = 36}\)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\question Explain multimedia and multimedia system. Explain data
stream characteristics with an appropriate figure.
\question Compare audio, music and sound. Explain the components of
speech recognition and understanding.
\question Explain how text is used in multimedia application. What is bit
map image? 
\question Define resource management architecture. Discuss the relation
between QoS and resource management. 
\question Why is the reference model for synchronization required and how
is it defined? Explain.
\question Define basic technology of optical storage media. Explain CD-
ROM extended architecture.
\question Write short notes on any TWO:
\begin{parts}
	\part Nyquist's sampling theorem
	\part Libraries and Toolkit
	\part Lossy compression algorithm
\end{parts}
 
\end{questions}
\newpage


%%%%%%Purbanchal University-2019%%%%%%
% 									 %															
%				2019				 %
%									 %
%%%%%%Purbanchal University-2019%%%%%%

\begin{framed}
	\raggedright{\bfseries\Large\centering PURBANCHAL UNIVERSITY \par {2019/ \textnp{२०७६}}\par}
	{ 4 Years Bachelor of Computer Application (BCA/Eighth Semester/Final)\par}
	{ Time: 3.00 hrs.  \hfill Full Marks: 60 / Pass Marks: 24\par}
	{\bfseries {BCA452CO, Multimedia Application \hfill}\par}
\end{framed}

{\noindent \it{Candidates are required to give their own answers in their own words as far as practicable.  }\par}
{\noindent \it{Figure in the margin indicate full marks.}\par}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\fullwidth{\centering \bfseries \underline{Group A}}}
{\hspace*{-0.5cm} \bfseries Answer TWO questions.} \hfill {\( \mathbf{2\times 12 =24}\)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}
  \question
  \begin{parts}
	  \part How multimedia is necessary in real world? Explain multimedia
	  with its classification.
	  \part What is data stream characteristics? Explain traditional data
	  stream characteristic in multimedia.
  \end{parts}

  \question Explain the types of image format in brief. Explain Image
  recognition steps with the help of block diagram.

  \question Why synchronization is required in multimedia? Explain with the
  help of example. How four layer referenced model explains the
  concept of synchronization?
	

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\fullwidth{\centering \bfseries \underline{Group B}}\par}
{\hspace*{-0.5cm}\noindent\bfseries Answer SIX questions.} \hfill {\( \mathbf{6 \times 6 = 36}\)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\question Define MIDI. Explain MIDI channel message and MIDI system
message.

\question Explain basic concepts of animation. Explain how animation can
be controlled?

\question Why do we need compression? Explain JPEG Audio Encoding in
brief.

\question What is multimedia operating system? Explain resource
management techniques in multimedia operating system.

\question Explain Abstraction level of programming with the help of the
block diagram.

\question Explain Group Communication Architecture used in multimedia
communication system.
\question Write short notes on any TWO:
\begin{parts}
		\part Video on demand
		\part Entropy Encoding
		\part Document Architecture
\end{parts}

\end{questions}

\end{document}